\chapter{Describing Fission Using Nuclear Density Functional Theory}\label{chap:Model}

(Nicolas gave a good annotated presentation in 2017 that describes some of the philosophy, as well as some of the outstanding challenges of spontaneous fission in an adiabatic framework: \verb|https://t2.lanl.gov/fiesta2017/school/Schunck_NotesSlides.pdf|)

Fundamentally, the assumption of adiabaticity is the assumption that collective and intrinsic degrees of freedom can be decoupled, and that the time-scale associated with collective degrees of freedom is slow compared to the time-scale of intrinsic (i.e. single-particle) motions of the system.

Today there are 2 microscopic approaches to fission in common use: time-dependent and static (time-independent) (or 3 models: time-dependent, static, and statistical). Time-dependent approaches evolve the system in real-time. Since fission is an inherently time-dependent process, these methods offer great insight into the fission process and the characteristics of the fragments \verb|\cite{Some TDHFB papers}|. However, they can only treat a single event at a time, making them impractical for estimating yields. Furthermore, despite efforts such as \cite{Bulgac2018}, there is currently no way to obtain a full yield distribution in a time-dependent framework.

On the other hand, static approaches assume that collective motion of the nucleus is slow compared to the motion of the intrinsic particles, and this assumption is used to create a potential energy surface in some space of collective shape coordinates. We can estimate fission yields in these approaches (see, for instance, \cite{Sadhukhan2016} along with our forthcoming paper on $^{294}$Og), but for practical reasons we are limited to describing complicated shapes in terms of just a few parameters, leading to uncertainty in the fragment properties. In particular, the part of the process at which the neck snaps and one nucleus becomes two, called scission, is not well-defined in static approaches.

This can be understood with an analogy: suppose we stretch a nucleus until a neck forms, and then we use a butcher knife to lop the two fragments apart. This works reasonably well for estimating fragment mass and charge, but it is very poor when it comes to estimating the relative energy of the fragments. To estimate fragment kinetic and excitation energies, one needs to carefully and delicately peel the interlocking fragments apart with a scalpel, or a proper accounting of entanglement and other many-body correlations.

In static approaches, scission is frequently characterized by a single number, corresponding to the number of particles in the neck. When that number falls below a certain predefined threshold, we say that the nucleus has scissioned. Fragments are identified and one can try to estimate the strength of the repulsive interaction forcing the fragments apart. Of course, as discussed by Younes and Gogny in \cite{Bonneau2007,Younes2011}, wavefunctions corresponding to individual nucleons may extend into the spatial region of the opposite fragment.

Our approach, which combines the Hartree-Fock-Bogoliubov (HFB) mean-field approximation to the energy with a many-body method inspired by Kohn-Sham density functional theory (DFT), is described below.

Spontaneous nuclear fission is a type of quantum tunneling; consequently, it should be described using quantum mechanics.

\section{Nuclear Density Functional Theory}
Since nuclei are quantum mechanical systems, they can in principle be described using the Schrodinger equation. However, in practice one finds this type of description difficult or impossible, for two reasons:

\begin{itemize}
\item In order to use the Schrodinger equation, one needs to know how to describe the interaction between particles, such as between protons and neutrons. However, protons and neutrons are made up of quarks and gluons, which interact via the strong nuclear force. Consequently, an analytic expression for the nucleon-nucleon interaction analogous to the $\frac{1}{r}$ form of the Coulomb interaction is not available. Finding different mathematical expressions which can describe the interaction between nucleons continues to be an active area of research \cite{lots of papers}
\item Even when an interaction is known, nuclei are large systems made up of many protons and neutrons. Solving the Schrodinger equation directly quickly becomes computationally intractable as the number of nucleons increases.
\end{itemize}

\subsection{Density Functional Theory}\label{sect:DFT}
Kohn-Sham DFT is based on the Hohenberg-Kohn theorems

Let us define the nucleon density in the following way: suppose we have a system described in second quantization by a set of creation and annhilation operators $c_i, c_i^\dagger$ which act on the [Fock-space?] vacuum state $\ket{\psi_0}$. The first Kohn-Sham theorem says that the energy of the system is a uniquely-defined functional of the density. That means that if a system of interacting particles and a system of noninteracting particles give the same density, the energy of those systems will be the same. This gives us the freedom to try to describe our system using a mean-field method instead of having to describe the pairwise interactions between every particle in the system - a huge simplification to the problem!

The second Kohn-Sham theorem states that the functional which gives the energy of the system will give the ground state energy if, and only if, it acts on the true ground state density. Thus, given a particular functional, we can vary the input density to minimize the total energy and be assured that we are approaching the ground state energy of the system.

Suppose you have the density $\rho(\mathbf{r})$ of an interacting system of particles. There exists a unique noninteracting system with the same density
Then I believe HFB is put on top of that to do the variation part. I think I (approximately) get it now! - So just to make sure, what would DFT look like without HF/HFB? And HF/HFB without DFT?

Rather than find the density of a system of interacting particles (which can be extremely complicated - as one particle moves, the force it exerts on neighboring particles causes them to move, which will in turn change the magnitude and direction of the net force acting on the original particle, and so on until an equilibrium configuration, if it exists, can be attained), Kohn-Sham allows us to find an equivalent density of fictional non-interacting particles. That is, instead of particles moving in a field generated by many interdependent neighboring particles, one may think of non-interacting particles moving about a mean-field, which is essentially an averaging over all other particles.

Together, the Hohenberg-Kohn theorems state that if one is able to find the true ground state density, regardless of where it comes from, then there exists a unique functional of the density which gives the ground state energy of the system. However, HK do not specify how this functional is to be obtained.

For a variety of reasons/complications (refs 73-78 of \cite{Schunck2016}), pure Kohn-Sham is not used in nuclear physics; however; in the spirit, we oftentimes switch to a representation involving densities (which are directly and exactly attainable from a many-body wavefunction) and energy density functionals (which are not known exactly). (Wait, but then what is the point of converting to densities? Why not just leave them as wavefunctions? Or maybe we do, but this representation just makes the math look nicer for papers)

The basic idea is to replace the single particle states $c_i^\dagger\ket{\psi_0}$ with the single-particle density, $\rho_{ij} = \expval{c_j^\dagger c_i}{\psi_0}$

Because pairing interactions are of great importance to nuclear dynamics, we also construct an additional density $\kappa_{ij} = \expval{c_jc_i}{\psi_0}$, which can be thought of as a coupling between the vacuum state and a state with two particles (in states $i$ and $j$). Together with the single-particle density $\rho$ we construct a generalized density

\begin{equation}
\mathcal{R} = \left(\begin{array}{cc}
\rho & \kappa \\
-\kappa^* & 1-\rho^*
\end{array}\right)
\end{equation}


[These will probably need to be brought into a more compliant form; make sure you've got the same notation everywhere in the thesis] (with q=isospin and $\sigma$=spin/signature quantum number)

\begin{align}
\rho_{q\sigma}(\mathbf{r}) &= \sum_{\alpha \in q} v_\alpha^2 \left|\psi_\alpha(\mathbf{r}\sigma)\right|^2 \\
\tau_{q\sigma}(\mathbf{r}) &= \sum_{\alpha \in q} v_\alpha^2 \left|\nabla\psi_\alpha(\mathbf{r}\sigma)\right|^2 \\
\mathbf{j}_{q\sigma}(\mathbf{r}) &= \sum_{\alpha \in q} v_\alpha^2 \mathrm{Im}\left[\psi^*_\alpha(\mathbf{r}\sigma)\nabla\psi_\alpha(\mathbf{r}\sigma)\right] \\
\nabla\rho_{q\sigma}(\mathbf{r}) &= 2\sum_{\alpha \in q} v_\alpha^2 \mathrm{Re}\left[\psi^*_\alpha(\mathbf{r}\sigma)\nabla\psi_\alpha(\mathbf{r}\sigma)\right] \\
\kappa &= ???
\end{align}


The total energy is a sum of several contributions:

\begin{equation}
E(\rho, \kappa) = E_{kin} + E_{Coul} + E_{nuc} + E_{pair}
%E(\rho, \kappa) = \int d^3\vec{r}\sum_{t=0,1}\mathcal{H}_t = \int d^3\vec{r}\left(\mathcal{H}_{kin} + \mathcal{H}_{nuc} + \mathcal{H}_{Coul, dir} + \mathcal{H}_{Coul, exch} + \mathcal{H}_{pair}\right)
\end{equation}

\noindent where $E_{kin}$ is the kinetic energy term, $E_{Coul}$ contains the Coulomb ineraction between protons, $E_{nuc}$ is a phenomenological nucleon-nucleon interaction term, and $E_{pair}$ describes the tendency of nucleons to form pairs, which is smeared out in non-interacting mean-field models. Finding a good nucleon-nucleon interaction $E_{nuc}$ (and to a lessert extent, $E_{pair}$) to use in calculations is an active topic of research in nuclear theory today (for one recent example, see \cite{NavarroPerez2018}); two types of interactions which are commonly-used today are the Skyrme and Gogny families of interactions \verb|\cite{???}|. We use primarily Skyrme-type interactions, which are described below.

\subsubsection{Kinetic term}

Defining $\tau_0$ as in eqn 10 of HFODD-I, the kinetic energy contribution is

\begin{equation}
E_{kin} = \frac{\hbar^2}{2m} \left(1-\frac{1}{A}\right) \int \tau(\vec{r}) d^3\vec{r}
\end{equation}

\subsubsection{Coulomb interaction}
The Coulomb interaction between protons is divided into a direct term and an exchange term, which is related to the Pauli exclusion principle.

\begin{align}
E_{Coul} &= E_{Coul, dir} + E_{Coul, exch} \\
E_{Coul, dir}& = \frac{e^2}{2} \int \frac{\rho_p(\vec{r}_1)\rho_p(\vec{r}_2)}{\abs{\vec{r}_1-\vec{r}_2}} d^3\vec{r}_1 d^3\vec{r}_2 \\
E_{Coul, exch} &= \frac{e^2}{2} \int \frac{\rho_p(\vec{r}_2,\vec{r}_1)\rho_p(\vec{r}_1,\vec{r}_2)}{\abs{\vec{r}_1-\vec{r}_2}} d^3\vec{r}_1 d^3\vec{r}_2
\end{align}

Often the exchange term is computed in the Slater approximation \verb|\cite{refs 27,28 of HFODD-I}|:

\begin{equation}
E_{Coul, exch} \approx -\frac{3e^2}{4} \left(\frac{3}{\pi}\right)^\frac{1}{3} \int\rho_p^\frac{4}{3}(\vec{r}) d^3\vec{r}
\end{equation}

\subsubsection{Skyrme interaction}
The total Skyrme interaction energy density is a sum of both time-even and time-odd terms:

\begin{align}
E_{Skyrme} &= \int \sum_{t=0,1} \left( \mathcal{H}^{even}_t + \mathcal{H}^{odd}_t \right) d^3\vec{r}\\
\mathcal{H}^{even}_t &= C^\rho_t\rho_t^2 + C_t^{\Delta\rho}\rho_t\Delta\rho_t + C^\tau_t\rho_t\tau_t + C^J_t\mathsf{J}^2_t + C^{\nabla J}_t\rho_t\nabla\cdot\vec{J}_t \\
\mathcal{H}^{odd}_t &= C^s_t \vec{s}_t^2 + C_t^{\Delta s}\vec{s}_t\Delta\vec{s}_t + C^T_t\vec{s}_t\cdot\vec{T}_t + C^j_t\mathsf{j}^2_t + C^{\nabla j}_t\vec{s}_t\cdot(\nabla\times\vec{j}_t)
\end{align}

\noindent where $\tau_t$ is the kinetic energy density; $\mathsf{J}_t$ is the spin current density, with vector part given by $\vec{J}_{\kappa,t} = \sum_{\mu\nu}\epsilon_{\mu\nu\kappa}\mathsf{J}_{\mu\nu,t}$; $\vec{s}_t$ is the spin density, $\vec{T}_t$ is the spin kinetic density; and $\vec{j}_t$ is the momentum density (to see how these are related to $\rho_t$, see, e.g., \cite{Bender2003}). The index $t=0(1)$ refers to isoscalar(isovector) energy densities. Note that $\mathcal{H}^{even}_t$ depends only on time-even densities (and likewise for $\mathcal{H}^{odd}_t$).

Since this interaction is phenomenological, based on a zero-range contact interaction between nucleons, the coefficients are adjustable. There are dozens of Skyrme parameterizations on the market, each one optimized to a particular observable or set of observables. The parameter sets SkM* \cite{Bartel1982} and UNEDF1 \cite{Kortelainen2012} (along with its sister, {\hfb} \cite{Schunck2015}) are optimized to datasets which include deformed nuclei, making them suitable for fission.

\subsubsection{Pairing interaction}
We use a density-dependent pairing interaction:

\begin{equation}
E_{pair} = V_0 \int \left( 1-\left(\frac{\rho(\vec{r})}{\rho_0}\right)^\alpha \right) d^3\vec{r}
\end{equation}

\noindent As with the nuclear interaction term, the pairing interaction contains several adjustable parameters.

\subsection{Bogoliubov transformation}

In anticipation of the HFB formalism below, we define the so-called Bogoliubov transformation. The fundamental entity in the Bogoliubov transformed basis are `quasiparticle' states, defined by quasiparticle creation and annhilation operators acting on a quasiparticle vacuum state $\ket{\Phi_0}$ (in contrast to the single particle operators from before). The creation and annhilation operators are given by

\begin{align}
\beta_\mu &= \sum_i U^*_{i\mu}c_i + \sum_i V^*_{i\mu}c_i^\dagger \\
\beta_\mu^\dagger &= \sum_i U_{i\mu}c_i^\dagger + \sum_i V_{i\mu}c_i
\end{align}

\noindent or in block matrix notation,

\begin{equation}
\left(\begin{array}{c} \beta \\ \beta^\dagger\end{array}\right) = 
\left(\begin{array}{cc} U^\dagger & V^\dagger \\ V^T & U^T \end{array}\right)
\left(\begin{array}{c} c \\ c^\dagger\end{array}\right)
\equiv \mathcal{W}^\dagger \left(\begin{array}{c} c \\ c^\dagger\end{array}\right)
\end{equation}

\noindent where the transformation matrix $\mathcal{W}$ must be unitary to ensure that $\beta, \beta^\dagger$ obey the fermion commutation relations \cite{Ring1980}. In this transformed basis, the density matrix takes the form 

\begin{equation}
\mathsf{R} = \mathcal{W}^\dagger\mathcal{R}\mathcal{W} = 
\left(\begin{array}{cc}
\expval{\beta_\mu^\dagger \beta_\nu}{\Phi_0} & \expval{\beta_\mu \beta_\nu}{\Phi_0} \\
\expval{\beta_\mu^\dagger \beta_\nu^\dagger}{\Phi_0} & \expval{\beta_\mu \beta_\nu^\dagger}{\Phi_0}
\end{array}\right) = 
\left(\begin{array}{cc}
0 & 0 \\
0 & I_N
\end{array}\right)
\end{equation}
... and the densities $\rho$ and $\kappa$ can be written ...

In general, $E$ is a functional of the generalized density $\mathcal{R}$.

\subsection{Hartree-Fock-Bogoliubov Equations}

The ground state configuration of the system described by this particular energy density functional $E$ is described by the density which minimizes $E(\mathcal{R})$. We can find this solution through the variational principle. We minimize the energy with respect to the generalized density, subject to the constraint that $\mathcal{R}^2=\mathcal{R}$, or in other words, that the state remains a quasiparticle vacuum. Defining the HFB Hamiltonian $\mathcal{H}_{ba} \equiv 2 \partial E/\partial \mathcal{R}_{ab}$, this variation leads to the result $\left[\mathcal{H},\mathcal{R}\right]=0$, which is called the Hartree-Fock-Bogoliubov equation. It is not typically solved in this form, but it can be recast into something more useful. Recalling that two Hermitian operators whose commutator is zero can be simultaneously diagonalized, we choose to diagonalize $\mathcal{H}$ using the same Bogoliubov transformation $W$ which diagonalizes $\mathcal{R}$:

\begin{equation}
W^\dagger \mathcal{H} W \equiv \mathcal{E} \qquad\mathrm{or}\qquad \mathcal{H}W = W\mathcal{E}
\end{equation}

\noindent where

\begin{equation}
\mathcal{E} = \left(\begin{array}{cc}
E_\mu & 0 \\
0 & -E_\mu
\end{array}\right)
\end{equation}

\noindent is a matrix of quasiparticle energies.
% https://ocw.mit.edu/courses/physics/8-04-quantum-physics-i-spring-2013/study-materials/MIT8_04S13_OnCommEigenbas.pdf

Very often we will want to minimize the energy with the system subject to a particular constraint. Some common examples might be this simple form of particle number restoration (more complicated forms, such as Lipkin-Nogami \verb|\cite{???}|, also exist)

\begin{equation}
\delta E' = \langle\Phi_0|\hat{H}-\lambda\hat{N}|\Phi_0\rangle
\end{equation}

\noindent or shape, where we might use a particular multipole moment (or set of multipole moments)

$\hat{H} - \lambda\hat{N} - \lambda_i \hat{Q}_i$

Lipkin-Nogami is related to this, but I forget exactly how at the moment: [Note: 14 November 2017] It turns out I'm not quite right about this. The ``pure HFB/static pairing case'' refers to the case described by $H' = H - \lambda N$. There are still (so far as I understand) dynamical pairing fluctuations. Then, once you add another term $H'' = H' + \lambda_2 \Delta N^2$ you'll obtain even stronger pairing fluctuations

\subsection{Collective inertia}
Just as important to the fission dynamics aas the energy of the system is the collective inertia, which describes the tendency of the system to resist configuration changes (such as shape changes). The form of the collective inertia we use is the non-perturbative adiabatic time-dependent HFB (ATDHFB) inertia with cranking, which takes the form (see the full temperature-dependent derivation in Appendix ???

\begin{equation}
\mathcal{M} = \dots
\end{equation}

A perturbative expression for the ATDHFB inertia also exists, which allows one to estimate the inertia without computing derivatives. It is computationally much faster and easier to implement, but it is less accurate and loses many of the important features of the inertia, as we shall see in Chapter ??? (294Og). Nevertheless, it is commonly-used in calculations and we shall use it later on.

Another common expression for the collective inertia comes from the Generator Coordinate Method (GCM). The GCM inertia also exists in two varieties: perturbative and non-perturbative \cite{Giuliani2018b}. Like the ATDHFB inertia, the perturbative GCM inertia is smoothed-out compared to the non-perturbative inertia. Both the perturbative and non-perturbative GCM inertias are found to be smaller in magnitude than their ATDHFB counterparts.

\subsection{Nucleon localization function}
One of the tools we will be using quite a bit in this thesis is the nucleon localization function (NLF), introduced in \cite{Zhang2016}. The NLF is defined using the single particle density in the following way (with q=isospin and $\sigma$=spin/signature quantum number):

\begin{equation}
\mathcal{C}_{q\sigma} = \left[1+\left(\frac{\tau_{q\sigma}\rho_{q\sigma}-\frac{1}{4}|\nabla\rho_{q\sigma}|^2-\mathbf{j}^2_{q\sigma}}{\rho_{q\sigma}\tau_{q\sigma}^{TF}}\right)^2\right]
\end{equation}

\noindent where $\tau_{q\sigma}^{TF}=\frac{3}{5}(6\pi^2)^\frac{2}{3}\rho_{q\sigma}^\frac{5}{3}$. A localization value $\mathcal{C} \approx 1$ means that nucleons are well-localized; that is, the probability of finding two nucleons of equal spin and isospin at the same location in space is low. A value of $\mathcal{C}=\frac{1}{2}$ corresponds to a Fermi gas of nucleons, as found in nuclear matter.

The NLF offers greater insight into the underlying shell structure of the system than, for instance, the single particle density. In particular, when applied to fission as in \cite{Sadhukhan2017}, it sometimes enables one to see the formation of well-defined prefragments whose shell structure is responsible for the peak of the fragment distribution.

\section{Microscopic Description of Nuclear Fission}
Should I describe these here, or in the sections when they actually get used?

With the nuclear physics somewhat under control, we now move onto the problem of using it to actually describe fission. For induced-fission, time-dependent density functional theory (TDDFT) allows one to calculate the time-evolution of a nucleus starting from some deformed initial configuration. So far, though, this approach has not been able to estimate a full yield for a fissioning nucleus; rather, the system propogates deterministically to a single scissioned configuration. Furthermore, and especially important for the case of spontaneous fission, the time-dependent approach does not allow for tunneling (why not?).

Nuclear fission is the fundamental physical process by which a heavy nucleus decays to two smaller nuclei with approximately equal masses, and a proper understanding of fission is critical for applications . It is a highly-collective process involving all the constituent nucleons of the system, and thus since its discovery it has been described via large shape deformations of an otherwise spherical ``drop'' of nucleons. In this framework, which is formalized by the adiabatic approximation, it falls upon theorists to describe many different nuclear shapes. In principle, one could describe any three-dimensional shape using an infinite basis such as the multipole expansion which is often encountered in eletrodynamics; however, for practical computations one must used a truncated set of only a few multipole moments (or, more generally, collective coordinates). Thus, an important challenge for researchers is to select the most relevant collective coordinates, ideally while demonstrating that others can be safely neglected.

Recently in \cite{Sadhukhan2016}, an approach based on this assumption was used to compute fragment yields from a potential energy surface (PES) that was computed self-consistently, using the WKB approximation to describe the tunneling and Langevin dynamics to describe post-scission dissipation. Now we test robustness of these results by exploring the impact of the energy density functional, the size of the collective space, and the calculation of the collective inertia on fragment yields.

\subsection{Potential Energy Surfaces}
Constrained HFB; map out many different constrained calculations and start to form a surface which resembles a topographical map. How do you decide which collective coordinates to use? Including pairing...

Physically, a nucleus can be thought of as a jumble of particles, each bouncing around in a potential well determined by the surrounding nucleons. Qunatum mechanics forbids us from determining the particle trajectories exactly; however, it allows us to estimate the probabilities of certain outcomes. In the case of fission, the most common approach has us thinking of nucleons grouping together collectively in a way which resembles a liquid drop (footnote: this idea was first proposed by Niels Bohr, I believe, and has proven to be a very fruitful way to describe fission). The collective shape is constrained to nearly-spherical shapes by a potential barrier; however, being a quantum mechanical system there is some nonzero tunneling probability, or a probability that the barrier will be penetrated, and the collective shape will stretch beyond the size fixed by the barrier. When this happens, the nucleus may remain in a long-term elongated state (called a fission isomer), or it may continue to deform until it separates into two fragments.

\subsection{WKB Approximation}

Adiabaticity: For fusion reactions, N,Z equilibrium reached in $\sim10^{-21}$ seconds, then energy/thermal equilibrium in a similar time scale, then finally mass equilibrium in $\sim10^{-19}$ - Yuri has a slide with these time scales from his talk Monday

Sort of an adiabatic approximation; useful because half-lives are long and therefore time-dependent approaches are impractical (they break down and/or become unstable or something after too many time steps, not to mention the amount of computing time). Wavefunction is assumed to be slowly-varying inside the potential barrier

Furthermore, TDHFB cannot tunnel

Consider a set of collective coordinates $\mathbf{q}\equiv(q_1, \ldots, q_N)$. In our implementation of the WKB
approximation, the most-probable tunneling path $\left. L(s) \right|_{s_{\rm
		in}}^{s_{\rm out}}$ in the collective space is found via minimization of the collective action
\begin{equation}\label{eq:action} 
S(L) = \frac{1}{\hbar}\int_{s_{\rm in}}^{s_{\rm out}} \sqrt{2\mathcal{M}(s)\left(V(s)-E_0\right)}ds,
\end{equation} 
where $s$ is the curvilinear coordinate along the path $L$,
$\mathcal{M}(s)$ is the collective inertia \cite{Sadhukhan2013} and $V(s)$ is
the potential energy along $L(s)$. $E_0$ stands for the collective ground-state
energy. The dynamic programming method \cite{Baran1981} is employed to determine
the path $L(s)$. The calculation is repeated for different outer turning points,
and each of these points is then assigned an exit  probability $P(s_{\rm out})=[1+\exp{(2S)}]^{-1}$ \cite{Baran1978}. 



\subsection{Langevin Dynamics}

After emerging from the classically-forbidden region of the PES, fission trajectories begin from the outer turning
line and then evolve along the PES according to the Langevin equations:
\begin{gather} 
	\frac{dp_i}{dt} =  
	-\frac{p_j p_k}{2} \frac{\partial}{\partial q_i}\left(\mathcal{M}^{-1}\right)_{jk} 
	- \frac{\partial V}{\partial q_i}  - \eta_{ij}\left(\mathcal{M}^{-1}\right)_{jk} p_k + g_{ij}\Gamma_j(t) \,, \\ 
	\frac{dq_i}{dt} = 	\left(\mathcal{M}^{-1}\right)_{ij} p_j \,,  
\end{gather} 
where $p_i$ is the collective momentum conjugate to $q_i$. The dissipation
tensor $\eta_{ij}$ is related to the random force strength $g_{ij}$ via the
fluctuation-dissipation theorem, and $\Gamma_j(t)$ is a Gaussian-distributed,
time-dependent stochastic variable.

The fluctuation-dissipation theorem is given by the expression $\sum_k g_{ik}g_{jk} = \eta_{ij}k_BT$. It effectively couples the collective and intrinsic via the system temperature, given by $k_BT = \sqrt{E^*/a}$ where $a=A/10$MeV$^{-1}$ parameterizes the level density and the excitation energy $E^* = V(s_{out}) - V(\mathbf{x}) - \frac{1}{2}\sum\left(\mathcal{M}^{-1}\right)_{ij}p_i p_j$.

It has been shown (Jhilam and Nicolas' paper) that fission yields are fairly robust with respect to the dissipation strength

Dissipation is treated in our work as a parameter, as a self-consistent description of dissipation is not yet known. However, work along this line has been started (maybe?) in refs 291-293 of \cite{Schmidt2018} (see section 4.1.1 for the context).